\sysfull

### 2017-11-13 paper/intro.tex
intro: draft of fig1

\begin{figure}
	%\includegraphics[width=\columnwidth]{figures/}
    \caption{\label{fig:coalesce}Task decomposition is required for intermittent execution but task transitions introduce overhead.}
\end{figure}

>>>>

\begin{figure}
	\includegraphics[width=0.9\columnwidth]{figures/coalescing-horiz}
    \caption{\label{fig:coalesce}Task coalescing at runtime reduces time and
energy overhead in task-based intermittent programming models by performing
fewer commits and buffering updates to non-volatile variables in volatile
memory.}
\end{figure}
